### 2009-09-09 latex/paper1/contents.tex
paper

We measured the similarity between each pair of software networks and then
calculated the average and the standard deviation. The average similarity was
0.97 and the standard deviation, 0.03. The high average similarity and the low
standard deviation show that software networks have common structural patterns
that are captured by the metric. The minimum similarity was 0.83.

@@

Then, for each non-software network, we measured the average similarity between
the network and all software networks. The majority of the networks (X\%) had an
average similarity lower than 0.83, which shows that they are ... Networks
extracted from the social network Facebook had negative similarities.

A few networks, though, showed high similarity to software networks. The network
polblogs, showing links between blogs on politics, had similarity 0.97. The
neural network of C Elegans also had a high similarity (0.88). Further
investigation is needed in order to discover why does it happen and whether
auxiliary metrics can differentiate these networks from software networks.

TODO: histogram of similarities? (maybe boxplot is enough)

@@

Although the similarity metric tells how close a network is from software
networks, it does not tell whether a network is close enough that it can be
considered a software network. Therefore, in this section we present a
classification model that splits networks into two classes: software-like
networks and non software-like networks.

@@

>>>>

Using the data set we can define the S-score of a network to be the average
similarity between the network and all 65 software networks. S-score summarizes
in a number between -1 and 1 how much a particular network resembles software
networks.

We measured the S-score for each software network and then calculated the
average and the standard deviation. The average S-score was 0.97 and the
standard deviation, 0.03. The high average S-score and the low standard
deviation show that software networks have common structural patterns that are
captured by the metric. The minimum S-score was 0.83.

@@

Then we measured the S-score for each non-software network. The majority of the
networks (X\%) have a S-score lower than 0.83, which shows that they
are ... Networks extracted from the social network Facebook have negative
S-score.

A few networks, though, showed high S-score. The network
polblogs, showing links between blogs on politics, had similarity 0.97. The
neural network of C Elegans also had a high similarity (0.88). Further
investigation is needed in order to discover why does it happen and whether
auxiliary metrics can differentiate these networks from software networks.

TODO: histogram of S-scores? (maybe boxplot is enough)

@@

Although the S-score of a network tells how close it is from software
networks, it does not tell whether a network is close enough that it can be
considered software-like. In order to do so we need to set a similarity
threshold, so

Therefore, in this section we present a classification
model that splits networks into two classes: software-like networks and non
software-like networks.

@@

First, we present a binary classification model / whether is software-like.
Then, we describe the procedure to synthesize networks, parameters choosed
After that, show results
Finally, build a classification model based on parameters
